---
title: 'R2 Reasonable Potential Tool Parameter Report'
date: "Compiled on `r format(Sys.time(), '%d %B, %Y')`"

# css: www/style.css
params:
  sdat: NA
  edat: NA
  NPDES: NA
  fac: NA
  street: NA
  citystate: NA
  outfall: NA
  param: NA
  unts: NA
  nsam: NA
  pmn: NA
  pmean: NA
  pmx: NA
  RWC: NA
  pcv: NA
  pz95: NA
  pzx: NA
  RPM: NA
  DR: NA
  WQSB: NA
  WQSD: NA
  pplot:
  dmrr:
output: pdf_document
header-includes: \usepackage{xcolor}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

\definecolor{maxcolor}{RGB}{223,194,125}
\definecolor{sbcolor}{RGB}{191,129,45}
\definecolor{sdcolor}{RGB}{140,81,10}
\definecolor{rwccolor}{RGB}{84,48,5}

# **`r params$NPDES` - `r params$outfall` : `r params$param`**

#### Evaluated from `r params$sdat` to `r params$edat`


### **FACILITY INFORMATION: **  

#### `r params$fac`
#### `r params$street`
#### `r params$citystate`

***
### **SUMMARY STATISTICS:**
#### Number of Samples: `r params$nsam` 
#### Min: `r params$pmn` `r params$unts` 
#### Mean: `r params$pmean` `r params$unts`
#### Max: `r params$pmx` `r params$unts` 
#### WQS - SB: `r params$WQSB` `r params$unts`
#### WQS - SD: `r params$WQSD` `r params$unts`
#### RWC: `r params$RWC` `r params$unts`


### **TIME SERIES**
# ```{r}
# params$pplot
# ```

#### &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp;\textcolor{maxcolor}{---Max: `r params$pmx` `r params$unts`} &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp;\textcolor{sbcolor}{...WQS - SB: `r params$WQSB` `r params$unts`}

#### &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; \textcolor{sdcolor}{- - WQS - SD: `r params$WQSD` `r params$unts`} &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp;\textcolor{rwccolor}{--RWC: `r params$RWC` `r params$unts`}

\newpage

### **RECEIVING WATER CONCENTRATION CALCULATIONS**
#### *assuming a 95% confidence level and a 95% probability basis*\
*calculations from 1991 Technical Support Document pgs 51-55*
\
\begin{align*}
\text {Number of samples} & = n\\
\text {Maximum effluent concentration} & = max\\
\text {Dilution Ratio} & = DR\\
\text {Coefficient of Variation (CV)} & = S_{n}/\mu \text { or 0.6 when n < 10}\\
\text {Z-statistic} & = Z_{x}\\
\text {Reasonable Potential Multiplier (RPM)} & = \displaystyle \frac{exp(Z_{95}\ln(1 + CV^{2})^{0.5} - 0.5\ln(1 + CV^{2}))}{exp(Z_{x}\ln(1 + CV^{2})^{0.5} - 0.5\ln(1 + CV^{2}))}\\
\text {Receiving Water Concentration} & = max * RPM / \text {Dilution Ratio}\\
\\
n & = `r params$nsam`\\
max & = `r params$pmx`\\
DR & = `r params$DR`\\
CV & = `r params$pcv`\\
Z_{95} & = `r params$pz95`\\
Z_{x} & = `r params$pzx`\\
\\
RPM & = \displaystyle \frac{exp(`r params$pz95`\ln(1 + `r params$pcv`^{2})^{0.5} - 0.5\ln(1 + `r params$pcv`^{2}))}{exp(`r params$pzx`\ln(1 + `r params$pcv`^{2})^{0.5} - 0.5\ln(1 + `r params$pcv`^{2}))}\\
 & = `r params$RPM`\\
 \\
RWC & = `r params$pmx` * `r params$RPM` / `r params$DR`\\
 & = `r params$RWC`
\end{align*}

***

\newpage

### **DATA TABLE**
```{r}
knitr::kable(params$dmrr)
```